|

### 2021-12-17 text/ManuscriptDraft.Rmd
Manusscript update

The tracking algorithm has a set of user adjusted parameters that can optimize tracking accuracy. The parameters are particularly relevant for optimal tracking of objects that are constrained to a specific area such as flowers. It is important to note, however, that the tracking algorithm can be used to track any objects. The tracking algorithm can be applied both offline (on a set of detections/annotations that have already been produced) or online (real-time tracking frame per frame). The speed of the tracking algorithm depends on the computational power available as well as the number of objects that are being tracked.

@@

Tracks that overlap have significant risk of errors. Overlapping tracks can be caused by a single flower that was erroneously assigned to several tracks, two flowers that were located sufficiently close to each other that there areas overlapped (e.g. when wind moves the flowers around), false positive detections close to a flower.Best case is two flowers that flowered in the same area but were separated by time. Here we will remove overlapping tracks to reduce the risk of error.

>>>>

The tracking algorithm has a set of user adjusted parameters that can optimize tracking accuracy. The parameters are particularly relevant for optimal tracking of objects that are constrained to a specific area such as flowers. It is important to note, however, that the tracking algorithm can be used to track any objects. The tracking algorithm can be applied both offline (on a set of detections/annotations that have already been produced) or online (real-time tracking frame per frame). The speed of the tracking algorithm depends on the computational power available as well as the number of objects that are being tracked. The method is fast, however. Tracking of a series containing 85 objects ran at 0.02 seconds per frame.

@@

Manually annotating a subset of the objects in the image series could help derive a good set of parameters.

When deploying the tracking algorithm on naive data that has not been manually tracked, it is not possible to

From our results we see that erroneous tracks often occur as small sections consisting of only few points within the main tracks.

Therefore, tracks that overlap have significant risk of errors. Overlapping tracks can be caused by a single flower that was erroneously assigned to several tracks, two flowers that were located sufficiently close to each other that there areas overlapped (e.g. when wind moves the flowers around), false positive detections close to a flower. Best case is two flowers that flowered in the same area but were separated by time. Here we will remove overlapping tracks to reduce the risk of error.

We could compare number of points in the overlapping tracks. If one is less than e.g. 10% of the other, we'll remove the small track. If more than 10% we'll remove both?
